IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-17 paper/retrofit.tex
save some space in figures

These asynchronous communication primitives are worth further
discussion.  When a task is sending a message using |send|, it also labels that
message with a label |il'| (which must be above the tasks current label |il|).
Messages can only be received by a task if its current label is
at least as high as the label of the message.
Specifically, receiving a message using
\[ |recvf ix1 ix2 ie1 ie2| \]
binds the message and the sender's task identifier
to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
Otherwise the message gets removed from the queue by rule \textsc{I-noRecv},
and that tasks continues its execution with |ie2|.
We denote the filtering of the message queue by |filter il Q|,
which is defined as follows.
If |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|, and otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more sensitive
than their current label would allow.

@@

\inferrule[I-getTaskId]
{ }
{|
niconf iS id il getTaskId
->
niconf iS id il id
|}

\and
\inferrule[I-getLabel]
{ }
{|
niconf iS id il getLabel
->
niconf iS id il il
|}

@@

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }

>>>>

These asynchronous communication primitives are worth further
discussion.  When a task is sending a message using |send|, it also labels that
message with a label |il'| (which must be above the tasks current label |il|).
Messages can only be received by a task if its current label is
at least as high as the label of the message.
Specifically, receiving a message using
$|recvf ix1 ix2 ie1 ie2|$
binds the message and the sender's task identifier
to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
Otherwise the message gets removed from the queue by rule \textsc{I-noRecv},
and that tasks continues its execution with |ie2|.
We denote the filtering of the message queue by |filter il Q|,
which is defined as follows.
If |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|, and otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more sensitive
than their current label would allow.

@@

\inferrule[I-getTaskId]
{ }
{|
niconf iS id il getTaskId
->
niconf iS id il id
|}
\hspace*{-0.5cm}

\and
\inferrule[I-getLabel]
{ }
{|
niconf iS id il getLabel
->
niconf iS id il il
|}
\hspace*{-0.5cm}

\and
\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }

@@
